The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays

### 2018-06-05 suppinfo.tex
june 5
Ralph's corrections included

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
%\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}

@@

\section{Core-excited states of Cl$^{-}$}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$^{-1}$4p, 1s$^{-1}$3d and 1s$^{-1}$5p core excitations in \ki~(lower panel) and \cli~(upper panel). The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
\label{fg:si_rdens_ions}
\end{figure}
%
%
The intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki. This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli. In the case of \ki, the excited electron mainly sees a $2/r$ potential. In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons. The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series. However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant. As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}. In contrast to this, the 3d and 5p states are not bound. % in the continuum.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%<<<<<<< HEAD:suppinfo.tex
\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous solution using tender x-rays}
%\title{Tracking the hazy boundary between resonant and normal Auger decay near the K-edges of aqueous \ki~and \cli}
%=======
\title{The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl}
%\title{Tracking the hazy boundary between resonant and normal Auger decay in near the K-edges of aqueous \ki~and \cli}
%>>>>>>> origin/master:suppinfo - Copy.tex

@@

\section{Core-excited states of Cl$^{-}$}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$^{-1}$4p, 1s$^{-1}$3d and 1s$^{-1}$5p core excitations in \ki~(lower panel) and \cli~(upper panel). The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
\label{fg:si_rdens_ions}
\end{figure}
%<<<<<<< HEAD:suppinfo.tex
%
%
The intensity of the Cl$^{-}$(1s$^{-1}$4p) state is lower than that of the \cli(1s$^{-1}$5p) state contrary to what is observed in \ki. This difference can be explained by the lower electron density of the 4p compared to the 5p electron in the region close to the core hole which thus results in the lower oscillator strength of the 1s$^{-1}$4p compared to the 1s$^{-1}$5p transition in \cli~(see Fig.\ \ref{fg:si_rdens_ions} in SI).
In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli. In the case of \ki, the excited electron mainly sees a $2/r$ potential. In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons. The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series. However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant. As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}. In contrast to this, the 3d and 5p states are not bound. % in the continuum.}
%=======

In what follows we give a simple explanation of the difference in the radial density distributions of the 1s$^{-1}$4p and 1s$^{-1}$5p states in \ki~and \cli. In the case of \ki, the excited electron mainly sees a $2/r$ potential. In addition, it sees a short range potential originating from the point-like nucleus and the screening electrons. The influence of the latter can be described by a quantum defect $\delta \ne 0$, which is almost constant for the entire infinite Rydberg series. However, in case of \cli~the outer electron does not experience a Coulomb potential and the short range potential becomes dominant. As a result of the absence of the Coulomb potential we see a different behavior in the properties of the states, like e.g.\ only a finite number of bound states (here obviously 4p) \citep{buckman94:539}. In contrast to this, the 3d and 5p states are not bound. % in the continuum.}

\begin{figure}
\centering
\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}. The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step. From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau_{c} l/d$, with $\tau_{c}$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.  The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
\label{fg:si_ct_time}
\end{figure}

%>>>>>>> origin/master:suppinfo - Copy.tex
